---
title: 'Assignment 3: Loops & case_when()'
author: "Quin Smith"
date: "2/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

### While loop: How many cups of brewed coffee would it take to die of a caffeine overdose? 

Open the .Rmd and run `ld_50()` on your weight in **pounds** to find out!  Example below uses 170 lbs to demonstrate.

This analysis is based on the LD50 of caffeine (the lethal dose amount of a substance that will kill 50% of the population).
The LD50 of caffeine is 150 mg of caffeine per kg of body weight.
 
```{r caffeine}
#source ld_50()
source(here("assignments/assignment_3/R", "ld_50.R"))

ld_50(170)
```

### Case_when():  Function to see if a car likely be ticketed or not based on speed

Run `speedr()` over a certain speed (mph) to see if you will/might get a ticket driving that fast in a 45 mph zone. 

```{r}
#source speedr()
source(here("assignments/assignment_3/R", "speedr.R"))

speedr(45)
speedr(75)
speedr(8)
```













